Supplementary material for\\ A Benchmark of Named Entity Recognition Approaches in Historical Documents\\ Application to 19$^{th}$ Century French Directories

### 2022-01-20 src-latex/parts/30-dataset.tex
Changed title of 3.1
Move evaluation-related content to dataset part

@@

\subsection{The  XIX\textsuperscript{th} century Parisian trade directories}

@@

>>>>

% Conventions nommage
% Dataset annoté à la main = "ground truth"
% ground truth aligné = "ner-reference"
% entrées pero aligné = "ner-pero"
% entrées tesseract alignées = "ner-tesseract"

@@

\subsection{A selection of Paris trade directories from 1798 to 1854}

@@

\subsection{Metrics proposed}

\Cref{fig.protocol} depicts the evaluation protocol used to assess the OCR and NER systems. Two quality evaluations
are performed in the pipeline, respectively named \emph{OCR Q.A.} and \emph{NER Q.A.}.

\textbf{OCR Q.A.} is performed after some text normalization of the OCR system outputs. Text normalization consists in
projecting Unicode characters onto the latin-1 \emph{charset} (whenever it makes sense) and removing extra symbols (hands,
crosses). Then, the predicted text is aligned with the reference text using standard tools from Stephen V. Rice's
thesis~\cite{santos.2019.wcmel,neudecker.2021.whdip} and the Character Error Rates (CER) are computed at the entry level
and at the global level.

\begin{align}
\mathrm{CER} &=  \frac{\#Errors}{\text{Reference Text Length}} & & \mathrm{CER}_\mathrm{norm} =  \frac{\#Errors}{\text{Alignment Length}} 
\end{align}

In this benchmark, we consider 3 OCR systems well known for historical document analysis: Pero OCR, Tesseract, and Kraken.

Next, a NER system extracts the named entities from the text of each entry output by the OCR and the \textbf{NER Q.A.}
is performed. The NER system outputs a text with tags that enclose the entities. To assess the quality of the entity
extraction, we rely on a technique similar as for the OCR evaluation. The predicted text is aligned with the reference
text and the tags are projected in the alignment. Then, the precision, recall, and f-measure (or f-score) are computed considering
only the exact matches between entities. Precision and recall are defined by equation (2); the f-measure is their harmonic mean.

\begin{align}
    \mathrm{precision} &= \frac{\text{\#exact matches}}{\text{\#entries in prediction}} & \mathrm{recall} &= \frac{\text{\#exact matches}}{\text{\#entries in reference}}
\end{align}

The whole process is illustrated on~\cref{fig.eval-ocr-ner}. The OCR text and the GOLD text are first aligned to
evaluate the OCR accuracy. As there are 11 mismatches over 56 aligned characters, the CER is thus 24\%. This alignment
is then used to back-project the GOLD tags to build the tagged NER reference string. Finally, the NER system runs on the
OCR text; its output is compared to the NER reference string. There is only 2 over 3 tags matching in the prediction (precision),
while only 2 over 4 entities are matched in the reference (recall). It follows an overall f-score of 0.4.

\begin{figure}[tb]
    \includegraphics[width=\linewidth]{figs/eval-ocr-ner.pdf}
    \caption{OCR and NER evaluation protocol example.}
    \label{fig.eval-ocr-ner}
\end{figure}

\joseph{TODO expliquer qu'il faut faire la fusion des sous-datasets NER}

First and foremost, to make sure that the datasets contain the same entries a preprocessing step must be performed.
Indeed, entries where the OCR produced an empty string and those for which no entity could be projected from the gold reference text are ignored.
To overcome this problem we filter each dataset by keeping only the entries common to all.
At the cost of losing  5\% of the gold references entries, we thus have four new annotated datasets containing the exact same entries.

### 2022-01-20 src-latex/parts/40-ocr-bench.tex
Move evaluation-related content to dataset part

\subsection{Dataset}
input: image crops for each entry
expected output: human transcription

8765 entries used, \joseph{FIXME number of chars}

\subsection{Metrics}
\textbf{OCR Q.A.} is performed after some text normalization of the OCR system outputs. Text normalization consists in
projecting Unicode characters onto the latin-1 \emph{charset} (whenever it makes sense) and removing extra symbols
(hands, crosses). Then, the predicted text is aligned with the reference text using standard tools from Stephen V.
Rice's thesis~\cite{santos.2019.wcmel,neudecker.2021.whdip}. The Character Error Rate (CER) is computed at the entry
level and at the global level defined as the ratio between the number of errors (insertions/deletions/substitutions)
over the reference text length.

\subsection{Systems/Variants under test}
In this benchmark, we consider 3 OCR systems well known for historical document analysis: Pero OCR, Tesseract, and Kraken.

@@

>>>>

@@

Dataset:
- input: image crops for each entry
- expected output: human transcription
- 8765 entries used, \joseph{FIXME number of chars}

Systems
In this benchmark, we consider 3 OCR systems well known for historical document analysis: Pero OCR, Tesseract, and Kraken.

### 2022-01-20 src-latex/parts/50-ner-xp1-training-set-size-and-pretraining.tex
Move evaluation-related content to dataset part

\subsection{Metrics}
Next, a NER system extracts the named entities from the text of each entry output by the OCR and the \textbf{NER Q.A.}
is performed. The NER system outputs a text with tags that enclose the entities. To assess the quality of the entity
extraction, we rely on a technique similar as for the OCR evaluation. The predicted text is aligned with the reference
text and the tags are projected in the alignment. Then, the precision, recall, and f-measure (or f-score) are computed considering
only the exact matches between entities. Precision and recall are defined by equation (2); the f-measure is their harmonic mean.

\begin{align}
    \mathrm{precision} &= \frac{\text{\#exact matches}}{\text{\#entries in prediction}} & \mathrm{recall} &= \frac{\text{\#exact matches}}{\text{\#entries in reference}}
\end{align}

>>>>

\subsection{Metrics}

### 2022-01-20 src-latex/parts/60-ner-xp2-pretraining-and-finetuning.tex
Update xp2 figure with bar value.
Move evaluation-related content to dataset part

\subsection{Dataset}

@@

First and foremost, to make sure that the datasets contain the same entries a preprocessing step must be performed.
Indeed, entries where the OCR produced an empty string and those for which no entity could be projected from the gold reference text are ignored.
To overcome this problem we filter each dataset by keeping only the entries common to all.
At the cost of losing  5\% of the gold references entries, we thus have four new annotated datasets containing the exact same entries.
They are denoted hereafter {reference, pero, tesseract}-gold.
Finally each is is split into a training, a dev and a test subset following the procedure presented in\cref{subsection:experiment-1-setup}.

\subsection{Metrics}
prec/recall/F1 as in \ref{sec:ner-xp1}

The whole process is illustrated on~\cref{fig.eval-ocr-ner}. The OCR text and the GOLD text are first aligned to
evaluate the OCR accuracy. As there are 11 mismatches over 56 aligned characters, the CER is thus 24\%. This alignment
is then used to back-project the GOLD tags to build the tagged NER reference string. Finally, the NER system runs on the
OCR text; its output is compared to the NER reference string. There is only 2 over 3 tags matching in the prediction (precision),
while only 2 over 4 entities are matched in the reference (recall). It follows an overall f-score of 0.4.

\begin{figure}[tb]
    \includegraphics[width=\linewidth]{figs/eval-ocr-ner.pdf}
    \caption{OCR and NER evaluation protocol example.}
    \label{fig.eval-ocr-ner}
\end{figure}

\subsection{Systems/Variants under test}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figs/eval-ner-exp2.pdf}
    \caption{F1 scores (in \%) of NER predictions in presence of OCR noise in the training and testing examples, either manually corrected or raw from Pero-OCR and Tesseract. The type of examples used to train the NER task is noted in indice after the model name (e.g. Bert$_{reference}$). Results show that best performances on OCRed entries are obtained when the BERT model has been pretrained and fine-tuned for NER on examples affected with similar OCR errors.}
    \label{fig:exp_2_eval_ner}
\end{figure}

>>>>

Dataset

@@

They are denoted hereafter {reference, pero, tesseract}-gold.
Finally each is is split into a training, a dev and a test subset following the procedure presented in\cref{subsection:experiment-1-setup}.

\joseph{préciser qu'on ne prend que les données qui sont valides pour pero et tesseract (soit 8341 entrées). On ne considère pas kraken car pas le temps, on perd 500 entrées dans l'intersection, la qualité est pourrie}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{images/experiment_2_f1_with_noise_graph.pdf}
    \caption{F1 scores (in \%) of NER predictions in presence of OCR noise in the training and testing examples, either manually corrected or raw from Pero-OCR and Tesseract. The type of examples used to train the NER task is noted in indice after the model name (e.g. Bert$_{reference}$). Results show that best performances on OCRed entries are obtained when the BERT model has been pretrained and fine-tuned for NER on examples affected with similar OCR errors.}
    \label{fig:exp_2_eval_ner}
\end{figure}
